---
title: "Customized Product Dasboard"
output: flexdashboard::flex_dashboard
runtime: shiny
---


```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(rmarkdown)
library(knitr)
library(Hmisc)
#library(tidyverse)
library(DT)
library(data.table)
library(shinyWidgets)
assignInNamespace("cedta.override", c(data.table:::cedta.override,"rmarkdown"), "data.table")


opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

```

```{r source_functions}
source("functions.R")
```


```{r constants}
source("constants.R")
```


```{r read_data}
dat <- fread(input = "~/Desktop/Columbia Fall 2021/Capstone/capstone_wd/HW3/Data/mobile phone survey data.csv", verbose = FALSE )

```

```{r customize_data}
dat.baseline <- unique(dat[, c("id", "Age", "Gender", "Income", "Region", "Persona")])
dat.baseline$income_group <- cut(dat.baseline$Income, breaks = c(0, 49999,74999, 99999,149999, 1000000000), labels = c("<50K", "50K-75k", "75K-100K","100K-150K", "150K+"))
dat.baseline$age_group <- cut(dat.baseline$Age, breaks = c(17,34,49,64,110), labels = c("18-34", "35-49", "50-64", "65+"))

dat$income_group <- cut(dat$Income, breaks = c(0, 49999,74999, 99999,149999, 1000000000), labels = c("<50K", "50K-75k", "75K-100K","100K-150K", "150K+"))
dat$age_group <- cut(dat$Age, breaks = c(17,34,49,64,110), labels = c("18-34", "35-49", "50-64", "65+"))
```

```{r variables}

unique.products <- dat[, unique(get(product.name))]
respondent.variables <- c(age_group.name, gender.name, income_group.name, region.name, persona.name) 
states.of.engagement <- c(awareness.name, consideration.name, consumption.name, satisfaction.name, advocacy.name)

age_group.variables <- unique(dat$age_group)
income_group.variables <- unique(dat$income_group)
gender_group.variables <- unique(dat$Gender)
region.variables <-unique(dat$Region)
persona.variables <- unique(dat$Persona)


bp.traits <- names(dat)[grep(pattern = bp.pattern, x = names(dat))]


positive_bp_traits <- bp.traits[1:8]
negative_bp_traits <- bp.traits[9:12]



```


Instructions
=====================================  

This application has 5 tabs that allows the user to investigate respondent demographics, product engagement, brand perceptions, outcome gaps, and linear/logistic regressions.  The user has complete control of the subgroups and outcomes used for each tab.  We recommend opening the application in your browser for optimal viewing experience. 

Q1 Respondent Demographics
===================================

Row {.sidebar}
-------------------------------------
Instructions:  Select a variable to customize graph that depicts the percentages of respondents in each category for that variable.  

```{r q1_input}
inputPanel(
  selectInput(inputId="respondent_variable", label = "Select Variable:", choices = respondent.variables, selected = respondent.variables[1]),
  checkboxInput(inputId = "respondent_show_percentages", label = "Show Percentages", value = TRUE)
)
```

Row {data-height=500}
-------------------------------------

```{r q1_output, fig.align='center'}

 renderPlot({
  tab <- percentage.table(x = dat.baseline[, .SD[1], by = id.name][, get(input$respondent_variable)])
  
  barplot(height = tab, space=0.1, las = 1, main = input$respondent_variable, ylab = "Percentage",
          xlab = input$respondent_variable, ylim = c(0, 1.2*max(tab, na.rm = TRUE)), col = "dodgerblue")
  
  if(input$respondent_show_percentages == TRUE){
    space_val = 0
    text(x = -0.4 + 1:length(tab) * (1+space_val), y = tab, labels = sprintf("%.1f%%", tab), pos = 3)
  }
})
```

Q2 Product Engagement
=====================================  


Row {.sidebar}
-------------------------------------
Instructions:  Select a single State of Engagement, and any combination of other variables, as long as at least one category from each variable is chosen.  
Additionally, select the number of products to display in decreasing order. 


```{r q2_input}


inputPanel(
  selectInput(inputId="ep_state", label = "Select State of Engagement:", choices = states.of.engagement, 
              selected = states.of.engagement[1]), 
    selectizeInput(inputId="income_group", label = "Select Income Group(s):", choices = c( income_group.variables),
                   selected = income_group.variables[1:5], multiple= TRUE),
      selectizeInput(inputId="age_group", label = "Select Age Group(s):", choices = c( age_group.variables), 
                     selected = age_group.variables[1:4], multiple = TRUE),
        selectizeInput(inputId="gender", label = "Select Gender(s):", choices = c(gender_group.variables), 
                       selected = gender_group.variables[1:2], multiple = TRUE),
          selectizeInput(inputId="region", label = "Select Region(s):", choices = c( region.variables), 
                         selected = region.variables[1:4], multiple = TRUE),
            selectizeInput(inputId="persona", label = "Select Persona(s):", choices = c(persona.variables),
                                 selected = persona.variables[1:6], multiple = TRUE),
              selectInput(inputId = "number", label = "Select Number of Products to Display", choices = 1:20, selected = 5)

  
)
```

Row {data-height=500}
-------------------------------------

```{r q2_output}

renderPlot({  

  
  
  numer <- dat[get(input$ep_state) == 1 & get(income_group.name) %in% input$income_group & get(age_group.name) %in% 
                 input$age_group & get(gender.name) %in% input$gender &  get(region.name) %in% input$region & get(persona.name) 
                  %in% input$persona ][, .(Num = .N), by = product.name]
  
  denoma <- dat[get(income_group.name) %in% input$income_group &  get(age_group.name) %in% input$age_group & get(gender.name) 
                  %in% input$gender &  get(region.name) %in% input$region & 
                    get(persona.name) %in% input$persona][get(input$ep_state) == 1 | get(input$ep_state) == 0][, .(Denom = .N), 
                                                                                                               by= product.name]
  
  
  rate = merge(numer, denoma, by = product.name)
  rate = rate[, Rate := Num/Denom *100, by = product.name]
  rate = rate[, lapply(X = .SD, FUN = "round.numerics", digits = 2)]
  rate = rate[, .(Product, Rate)]
  setorderv(x = rate, cols = "Rate", order = -1)
  xx= rate[1:input$number]
  
  p <- ggplot(xx, aes(x = reorder(Product, -Rate), Rate)) + geom_bar(stat = "identity", fill = "dodgerblue") + labs(x = "Product", y = "Rate (%)") + ggtitle("Top Products")
  
 p + expand_limits(y = c(0,100))

  })
    


```


Q3 Overall Brand Perceptions 
=====================================  


Row {.sidebar}
-------------------------------------
Instructions: Select any combination of variables, as long as at least one category from each variable is chossten.  
Additionally, select the number of products to display in decreasing order. 
```{r q3_input}
inputPanel(
   selectizeInput(inputId="income_group1", label = "Select Income Group(s):",  choices = c(income_group.variables), 
                  selected = income_group.variables[1:5], multiple= TRUE),
      selectizeInput(inputId="age_group1", label = "Select Age Group(s):", choices = c( age_group.variables), 
                     selected = age_group.variables[1:4], multiple = TRUE),
        selectizeInput(inputId="gender1", label = "Select Gender(s):", choices = c(gender_group.variables),
                       selected = gender_group.variables[1:2], multiple = TRUE),
          selectizeInput(inputId="region1", label = "Select Region(s):", choices = c( region.variables),
                         selected = region.variables[1:4], multiple= TRUE),
            selectizeInput(inputId="persona1", label = "Select Persona(s):", choices = c(persona.variables),
                                 selected = persona.variables[1:6], multiple = TRUE),
              numericInput(inputId = "choices",label = "Input # of Brands", value = 5, min = 1, max = 20, step = 1)
  
  
)
```

Row {data-height=500}
-------------------------------------

```{r q3_output}


renderPlot({


inputdat <- dat[get(income_group.name) %in% input$income_group1 & get(age_group.name) %in% input$age_group1 & get(gender.name) %in% input$gender1 &  get(region.name) %in% input$region1 & 
                  get(persona.name) %in% input$persona1 ]


positive.perception1 <- inputdat[, lapply(X = .SD, FUN = "mean", na.rm = TRUE), .SDcols = bp.traits, by = Product][, .SD, .SDcols = positive_bp_traits, by = Product]

negative.perception1 <- inputdat[, lapply(X = .SD, FUN = "mean", na.rm = TRUE), .SDcols = bp.traits, by = Product][, lapply(X = .SD, FUN = "invert_func"), .SDcols = negative_bp_traits, by=Product]

all.perceptions1 <- merge(positive.perception1,negative.perception1)

top5_avg_perception1 <- all.perceptions1[, "Average_Perception" := rowMeans(.SD), .SDcols = bp.traits][order(-rank(Average_Perception))][1:input$choices,.(Product, Average_Perception)][, lapply(X = .SD, FUN = "round.numerics", digits = 2)]

w <- ggplot(top5_avg_perception1, aes(x = reorder(Product, -Average_Perception), Average_Perception)) + geom_bar(stat = "identity", fill = "dodgerblue") + labs(x = "Product", y = "Average") + ggtitle("Top Products")

  w + expand_limits(y = c(0,10))

})
```


Q4 Outcome Gaps 
=====================================  

Row {.sidebar}
-------------------------------------
Instructions:  Select two outcomes to visualize the ranks of products in terms of the difference in averages between the them.  
The difference in rates is the Average First Outcome - Average Second Outcome per product.
Select the number of top products to display.  
Select to have barplot display percentages for each product.
Select number of digits for the percentages to be rounded to.  1 digit would be like 61.1%,

```{r q4_input}

inputPanel(
  selectInput(inputId="outcome", label = "Select Outcome:", choices = states.of.engagement, selected = advocacy.name),
    selectInput(inputId="outcome1", label = "Select Outcome:", choices = states.of.engagement, selected = satisfaction.name),
      selectInput(inputId = "number1", label = "Select Number of Products to Display", choices = 1:20, selected = 5),
        checkboxInput(inputId = "show_per", label = "Show Percentages", value = TRUE),
            sliderInput(inputId = "digits", label = "Select Digits To Round", min = 0, max = 5, value = 1, step = 1)

)
```

Row {data-height=500}
-------------------------------------

```{r q4_output}
# if else needed to calculate outcome on correct scale, depending on which outcome is selected first 


renderPlot({

  
  if(input$show_per == TRUE){
    
    
    
  if(input$outcome1 == 'Satisfaction'){

  x1 <- dat[, .(X1 = mean(get(input$outcome), na.rm = TRUE)), by = Product]
  x2 <-dat[, .(X2 = mean(get(input$outcome1), na.rm = TRUE)/10), by = Product]
  mer <- merge(x1, x2)
  
  Gap_df <- mer[, .(Gap = (X1 - X2)*100), by = Product]
  setorderv(x = Gap_df, cols = "Gap", order = -1)
  xx <- Gap_df[1:input$number1]
  ll <- round((xx$Gap), input$digits)

  ggplot(xx, aes(x = reorder(Product, -Gap), Gap)) + geom_bar(stat = "identity", fill = "dodgerblue") + labs(x = "Product", y = "Gap" ,title = "Top Products with Largest Gap")+  geom_label(label =ll)
    
  } 
    
    
    else  if(input$outcome == "Satisfaction"){
  
  x1 <- dat[, .(X1 = mean(get(input$outcome), na.rm = TRUE)/10), by = Product]
  x2 <-dat[, .(X2 = mean(get(input$outcome1), na.rm = TRUE)), by = Product]
  mer <- merge(x1, x2)
  
  Gap_df <- mer[, .(Gap = (X1 - X2)*100), by = Product]
  setorderv(x = Gap_df, cols = "Gap", order = -1)
  xx <- Gap_df[1:input$number1]  
  ll <- round((xx$Gap), input$digits)

  ggplot(xx, aes(x = reorder(Product, -Gap), Gap)) + geom_bar(stat = "identity", fill = "dodgerblue") + labs(x = "Product", y = "Gap" ,title = "Top Products with Largest Gap") +  geom_label(label = ll)

  
  } 
    
    
    else {
    
  x1 <- dat[, .(X1 = mean(get(input$outcome), na.rm = TRUE)), by = Product]
  x2 <-dat[, .(X2 = mean(get(input$outcome1), na.rm = TRUE)), by = Product]
  mer <- merge(x1, x2)

 Gap_df <- mer[, .(Gap = (X1 - X2)*100), by = Product]
  setorderv(x = Gap_df, cols = "Gap", order = -1)
  xx <- Gap_df[1:input$number1]   
    ll <- round((xx$Gap), input$digits)

  ggplot(xx, aes(x = reorder(Product, -Gap), Gap)) + geom_bar(stat = "identity", fill = "dodgerblue") + labs(x = "Product", y = "Gap" ,title = "Top Products with Largest Gap") + geom_label(label= ll)

          }
  
  } 
  
  
  else{
    
    
  if(input$outcome1 == 'Satisfaction'){

  x1 <- dat[, .(X1 = mean(get(input$outcome), na.rm = TRUE)), by = Product]
  x2 <-dat[, .(X2 = mean(get(input$outcome1), na.rm = TRUE)/10), by = Product]
  mer <- merge(x1, x2)
  
  Gap_df <- mer[, .(Gap = (X1 - X2)*100), by = Product]
  setorderv(x = Gap_df, cols = "Gap", order = -1)
  xx <- Gap_df[1:input$number1]
  #ll <- round((xx$Gap), input$digits)

  ggplot(xx, aes(x = reorder(Product, -Gap), Gap)) + geom_bar(stat = "identity", fill = "dodgerblue") + labs(x = "Product", y = "Gap" ,title = "Top Products with Largest Gap") 
    
  } 
    
    
    else  if(input$outcome == "Satisfaction"){
  
  x1 <- dat[, .(X1 = mean(get(input$outcome), na.rm = TRUE)/10), by = Product]
  x2 <-dat[, .(X2 = mean(get(input$outcome1), na.rm = TRUE)), by = Product]
  mer <- merge(x1, x2)
  
  Gap_df <- mer[, .(Gap = (X1 - X2)*100), by = Product]
  setorderv(x = Gap_df, cols = "Gap", order = -1)
  xx <- Gap_df[1:input$number1]  
  #ll <- round((xx$Gap), input$digits)

  ggplot(xx, aes(x = reorder(Product, -Gap), Gap)) + geom_bar(stat = "identity", fill = "dodgerblue") + labs(x = "Product", y = "Gap" ,title = "Top Products with Largest Gap") 

  
  } 
    
    
    else {
    
  x1 <- dat[, .(X1 = mean(get(input$outcome), na.rm = TRUE)), by = Product]
  x2 <-dat[, .(X2 = mean(get(input$outcome1), na.rm = TRUE)), by = Product]
  mer <- merge(x1, x2)

 Gap_df <- mer[, .(Gap = (X1 - X2)*100), by = Product]
  setorderv(x = Gap_df, cols = "Gap", order = -1)
  xx <- Gap_df[1:input$number1]   
  #  ll <- round((xx$Gap), input$digits)

  ggplot(xx, aes(x = reorder(Product, -Gap), Gap)) + geom_bar(stat = "identity", fill = "dodgerblue") + labs(x = "Product", y = "Gap" ,title = "Top Products with Largest Gap")
    
  }
  
    
  }
  
   
})


```


Q5 Models
=====================================  

Row {data-height=500}
-------------------------------------


```{r q5_input}

inputPanel(
  selectInput(inputId="em_state", label = "State of Engagement:", choices = states.of.engagement, selected = states.of.engagement[1]),
    selectInput(inputId="em_product", label = "Brand", choices = unique.products, selected = unique.products[1], multiple = TRUE),
       selectInput(inputId="em_inputs", label = "Choose Inputs:", choices = c(age_group.name, gender.name, region.name, income_group.name, persona.name, bp.traits), selected = c(age_group.name, gender.name, region.name, income_group.name), multiple = TRUE),
  selectInput(inputId="em_age_group", label = "Age", choices = age_group.variables, selected = age_group.variables, multiple = TRUE),
  selectInput(inputId = "em_gender", label = "Gender", choices = gender_group.variables, selected = gender_group.variables, multiple = TRUE),
  selectInput(inputId = "em_income_group", label = "Income", choices = income_group.variables, selected = income_group.variables, multiple = TRUE),
  selectInput(inputId = "em_region", label = "Region", choices = region.variables, selected = region.variables, multiple = TRUE),
  selectInput(inputId = "em_persona", label = "Persona", choices = persona.variables, selected = persona.variables, multiple = TRUE)
)
```

Row {data-height=500}
-------------------------------------

```{r q5_output}
renderDataTable({
  subdat <- dat[get(product.name) %in% input$em_product & get(age_group.name) %in% input$em_age_group & get(gender.name) %in% input$em_gender & get(income_group.name) %in% input$em_income_group & get(region.name) %in% input$em_region & get(persona.name) %in% input$em_persona]
  
  if(input$em_state == satisfaction.name){
    model.type <- "linear"
  }
  if(input$em_state != satisfaction.name){
    model.type <- "logistic"
  }
  
  res <- fit.model(dt = subdat, outcome.name = input$em_state, input.names = input$em_inputs, model.type = model.type)
  
  datatable(data = res)
})
```

